MLB Team Statistics between 2000 - 2023 on Predicting Games Won per Season ^[Code and data are available at: https://github.com/YcartXin/MLB_Team_Stats]

### 2024-04-08 paper/paper.qmd
Added tests for simulated data, added more data frames.

Important statistics for a team in this paper is defined as the team's batting average (AVG), defensive efficiency ratio (DffEff), and earned run average (ERA). These three statistics each refer to an important aspect of a strong team: hitting, pitching, and fielding prospectively. The specifics of these indicators will be elaborated on in @sec-data. Among present research, 2024 season predictions exist, however, they mainly focus on the win for a game or series for betting purposes. This paper is unique in its approach to predict and investigates the predictability of overall seasonal wins for baseball teams.

The rest of the paper is structured as follows. @sec-data (Data) will explain the source of the data used, its collection process, and the process of cleaning that led to the final data used as well as potential biases. @sec-model...

@@

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

>>>>

Important statistics for a team in this paper is defined as the team's batting average (AVG), defensive efficiency ratio (DffEff), and earned run average (ERA). These three statistics each refer to an important aspect of a strong team: hitting, pitching, and fielding prospectively, hence important indicators on the wins a team is predicted to earn in a season. The specifics of these indicators will be elaborated on in @sec-data. Among present research, 2024 season predictions exist, however, they mainly focus on the win for a game or series for betting purposes. This paper is unique in its approach to predict and investigates the predictability of overall seasonal wins for baseball teams.

The rest of the paper is structured as follows. @sec-data (Data) will explain the source of the data used, its collection process, and the process of cleaning that led to the final data used. The data section will also explore the potential biases the collected and final data may possess. @sec-model...

@@
